The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-15 talk/vmil2012/paper.tex
this is actually done
more project-internal citations

\todo{the introduction needs some work}
\cfbolz{the first two two paragraphs talk about deoptimization, then it
switches to guards. I would say we should only talk about guards in the
beginning}

@@

The RPython language and the PyPy project were started in 2002 with the goal of
creating a Python interpreter written in a high level language, allowing easy
language experimentation and extension. PyPy is now a fully compatible
alternative interpreter for the Python language.
Using RPython's tracing JIT compiler it is on average about 5 times faster than
CPython, the reference implementation.
PyPy is an interpreter written in RPython and takes advantage of the language
features provided by RPython
such as the provided tracing just-in-time compiler described below.

@@

RPython provides a tracing JIT that can be reused for a number of language
implementations. This is possible, because it traces the execution of the
language interpreter instead of tracing the user program directly. This
approach is called \emph{meta-tracing}. For the purpose of this paper the fact
that RPython's tracing JIT is a meta-tracing JIT can be ignored.

>>>>

@@

The RPython language and the PyPy project~\cite{rigo_pypys_2006} were started
in 2002 with the goal of
creating a Python interpreter written in a high level language, allowing easy
language experimentation and extension. PyPy is now a fully compatible
alternative interpreter for the Python language.
Using RPython's tracing JIT compiler it is on average about 5 times faster than
CPython, the reference implementation.
PyPy is an interpreter written in RPython and takes advantage of the language
features provided by RPython
such as the provided tracing just-in-time compiler described below.

@@

RPython provides a tracing JIT that can be reused for a number of language
implementations~\cite{bolz_tracing_2009}. This is possible, because it traces
the execution of the
language interpreter instead of tracing the user program directly. This
approach is called \emph{meta-tracing}. For the purpose of this paper the fact
that RPython's tracing JIT is a meta-tracing JIT can be ignored.
The only point of interaction is that some of the guards that are inserted into
the trace stem from an annotation provided by the interpreter
author~\cite{bolz_runtime_2011}.
